Tables/Graphs for Article

### 2017-12-15 article submission/graphics.Rmd
edited rounding on tables

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 4) + rcs(log10(text_length), 5) +
                   rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
```

### Univariate analysis results (Table 2) see univariate_analysis file

@@

@@

options(scipen=999)
univ_results <- univ_results %>% arrange(pvalue)

@@

  f3 <- paste("Surv(time_until_answer, answered) ~ rcs(", var, ", 3)", sep = "")
  k3 <- cph(stats::as.formula(f3), data = train1)
  df3 <- data.frame(variable = "3 knots", 
                   pvalue = unname(k3$stats[5]), 
                   AIC = AIC(k3, k = 2))
  return(rbind(df, df5, df4, df3))
}
# ---------------------------------------------------------------------------------------
txt <- fit_splines("log10(text_length)") # 3 knots or none
newline <- fit_splines("sqrt(newline_ratio)") # 3 knots
tagscore <- fit_splines("sqrt(avg_tag_score)") # 5 knots or none 
device <- fit_splines("sqrt(device_length)") # 5 knots
taglength <- fit_splines("sqrt(avg_tag_length)") # 4 knots
txt
newline
tagscore
device
taglength

@@

xtable::xtable(splinedf, caption = "Determining the optimal number of splines for each predictor", label = "table:splines")
```

@@

  train[["predictions"]] <- exp(predict(model, type = "lp"))
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

@@

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             R2 = round(metric$stats[8], 2),
                             AIC = stats::AIC(metric1, k = 2),
                             Dxy = round(metric1$stats[9],2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

@@

cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
avg_results1 <- get_avgmetrics(cv_results1)
avg_results1
xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv")
```

@@

modelstats <- data.frame(statistic = names(model$stats), 
                         value = round(unname(model$stats), 3))
modelstats
# ------------------------------------------

@@

metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)
AIC(metric, k = 2) # 83124.21

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2),
                              R2 = round(metric$stats[8], 2),
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = round(metric$stats[9],2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics

>>>>

### Model on full data

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 4) + rcs(log10(text_length), 5) +
                   rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
model
```

### Univariate analysis results

@@

c_pvalue <- c_pvalue %>% arrange(pvalue)

@@

univ_results <- univ_results %>% arrange(pvalue)

@@

  f3 <- paste("Surv(time_until_answer, answered) ~ rcs(", var, ", 3)", sep = "")
  k3 <- cph(stats::as.formula(f3), data = train1)
  df3 <- data.frame(variable = "3 knots", 
                   pvalue = unname(k3$stats[5]), 
                   AIC = AIC(k3, k = 2))
  return(rbind(df, df5, df4, df3))
}
# ---------------------------------------------------------------------------------------
txt <- fit_splines("log10(text_length)") # 3 knots or none
newline <- fit_splines("sqrt(newline_ratio)") # 3 knots
tagscore <- fit_splines("sqrt(avg_tag_score)") # 5 knots or none 
device <- fit_splines("sqrt(device_length)") # 5 knots
taglength <- fit_splines("sqrt(avg_tag_length)") # 4 knots

@@

xtable::xtable(splinedf, caption = "Determining the optimal number of splines for each predictor", label = "table:splines", digits = -16)
```

@@

  train[["predictions"]] <- exp(predict(model, type = "lp"))
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = metric$stats[3], 
                              pval = metric$stats[5],
                              R2 = metric$stats[8],
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = metric$stats[9], 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

@@

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = metric1$stats[3], 
                             pval = metric1$stats[5], 
                             R2 = metric$stats[8],
                             AIC = stats::AIC(metric1, k = 2),
                             Dxy = metric1$stats[9], 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

@@

cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
avg_results1 <- get_avgmetrics(cv_results1)
avg_results1
xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv", digits = 4)
```

@@

modelstats <- data.frame(statistic = names(model$stats), 
                         value = round(unname(model$stats), 3))
modelstats

@@

metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = x)

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = metric$stats[3], 
                              pval = metric$stats[5],
                              R2 = metric$stats[8],
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = metric$stats[9], 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics
xtable::xtable(final_metrics, caption = "Performance metrics for model fit to the full data", label = "table:finalmetrics", digits = 4)
